NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models: Supplemental Materials

### 2018-06-09 paper/itemizedReviewResponse.tex

R1:
+ interesting topic
+ usage scenarios are interesting
- description of NLP NN and attention models are not sufficiently detailed in the paper
- details of collaboration with domain experts are missing
- justification of tasks are not sufficiently detailed
- differences between graph and matrix view should be explained in more detail
- density contour in the prediction view needs to be explained in more detail
- claims about extension of visualization system to non-NLI tasks is not supported
- need to clarify difference between proposed perturbation-driven analysis and gradient-based analysis
- qualitative evaluation is weak

R2:
+ important area for visualization research
+ article is well-written
+ application with linked views is well-designed and powerful
+ system supports debugging of inference models
- scalability of system is not discussed

R3:
- article is dense and difficult to read
- rationale for design choices are not clear
- core contributions are not highlighted, too much emphasis on background material (explanation of NLI), not enough on the visualization system itself
- claims based on user evaluation aren?t supported

Reviewer 1

Acceptable
Justification
This paper presents an interactive visualization system for analyzing natural language inference models with attention mechanisms. The perturbation-driven paradigm proposed by the authors are well implemented with various visualization components. However, there is still room to improve the presentation of the task analysis and the system design. The contribution of the visualization tool is limited to NLI models and it?s unclear how it could be extended to support the analysis of other tasks/models.
The Review

Q1. The usage scenarios also look interesting, especially the Scenario 3. Does the result to some extent suggest that the attention mechanism is not a very efficient component in this task? I expect the authors dig it further.

Q2. In Section 2, the neural net in NLP and attention mechanisms are introduced. But the descriptions are unsatisfactory. There is no formal definition or description of the model and the attention mechanism. It's still unclear how the attention mechanism is applied in the model. I would suggest the authors include a concise and formal introduction in the background part and include some formula.

Q, In Section 4, the paper indicates that the system is developed under a long-term collaboration with NLP experts, but there is no description describing the details of the collaboration (the number of experts, the length and the form of the collaboration, the frequency of the meetings). It?s not until Section 7 did I learn that there are 2 NLP experts in collaboration. The task analysis can also be improved by including more detailed justification of the three tasks.

Q The presentation of the system design in Section 5 could be improved.
- In Section 5.2, Attention View include both a bipartite graph and a matrix view, which visualize the same information. From the description of the paper, the graph view is only good for highlighting the most dominant alignments. I suspect that matrix view can also reveal the most dominant alignments by identifying the most salient color. Please justify the design decision.

Q, It's unclear how the simplification of attention representation is done from Section 5.2, please include more details.

Q, In Section 5.3, how do you compute the density contour? Why is a contour needed in the analysis?

Q, It's better if the authors present the relation between Section 5.3 and 5.4 in a clearer way. It?s confusing to read how one can perturb a prediction in Section 5.3 before he/she read the algorithm in Section 5.4. I suggest put the algorithm along with the perturbation-driven paradigm at the beginning of Section 5

Q Except for the presentation issue, the contribution of this paper is somewhat limited to only NLI models with attention mechanisms. It's not sure how the visualization can be easily extended for other NLP tasks. For example, I am not sure how the proposed visualization can easily adapt to machine translation, considering that there are no neutral/contradiction/entailment labels.

A: The composability of the system is the key to extend its capability

Q, In addition, the perturbation-driven scheme is somewhat related to the gradient-based analysis (both are the local analysis of the model on a specific prediction). It is better if the authors discuss the two and differentiate them.

A: connection with sensitivity analysis

Q, The evaluation is acceptable but a bit weak. There is no description of what questions have the authors asked during the evaluation sessions. It would be better to have formal interviews and ask the participants to perform specific tasks and observe how they performed.

Please also proofread the work and fix typos. For example, the word 'work' in Section 3 should be uncountable; In Section 5.3, "the three points defines a triangle" -> "the three points defining a triangle"

The Review

The authors propose a system to debug the predictions of deep inference models in language domain.
These models focus on predicting whether a hypothesis entails, contradicts, or is neutral to a given premise.
This is a very essential task in natural language understanding that goes beyond machine translation where the models transform an input language to an output language without being able to evaluate logical entailment between sentences nor to answer questions based on given text.

The system is very well designed and the article is very well written.
The authors employ five linked views to show different facets about the model at varying granularity and at stages in the model pipeline. The visualization design in each of these views is mapped smoothly from the data it shows and the analysis task it serves.

Likewise, the linkage between these views and the corresponding interactions are well suited for debugging purposes. In particular:
- they enable tracing the root cause of certain entailment predictions e.g. by exposing the model attention computed at any selected part of an input sentence.
- they enable examining different perturbations of the input sentence and easily identifying the ones that lead to changes in the prediction, hence revealing the language features behind these predictions and the corresponding attention values computed by the model.
- they enable reducing visual clutter by interactively collapsing irrelevant parts, which improves resolution.
Furthermore, the authors provide auxiliary helps such as grammar dependency tree and a diff heatmap.

### 2018-06-09 paper/prediction.tex
fix typos

\subsection{Prediction View}
\label{sec:prediction}
For a given sentence pair, the model predicts a discrete probability distribution of the three labels (neutral, contradiction, and entailment).
%
In the prediction view, as illustrated in Fig.~\ref{fig:predictionView}(a), a prediction probability is encoded as a point in the barycentric coordinate system of the triangle. 
Let $\mathbf{C_1}$,$\mathbf{C_2}$,$\mathbf{C_3}$ be the three points defines a triangle, and let $p_1$, $p_2$, $p_3$ be the probabilities the label is neutral, contradiction or entailment. The coordinate of the prediction $\mathbf{C_p}$ in the triangle is computed as $\mathbf{C_p} = p_1\mathbf{C_1}+p_2\mathbf{C_2}+p_3\mathbf{C_3}$.
In the triangle, the distinctly colored background (grey, light grey, and light green) indicates the regions that correspond to different labels. The prediction result for the original sentence pair is represented by the larger yellow circle, whereas the smaller gray circles illustrate the perturbed sentence pairs. A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.

>>>>

\subsection{Prediction View}
\label{sec:prediction}
For a given sentence pair, the model predicts a discrete probability distribution of the three labels (neutral, contradiction, and entailment).
%
In the prediction view, as illustrated in Fig.~\ref{fig:predictionView}(a), a prediction probability is encoded as a point in the barycentric coordinate system of the triangle. 
Let $\mathbf{C_1}$,$\mathbf{C_2}$,$\mathbf{C_3}$ be the three points defining a triangle, and let $p_1$, $p_2$, $p_3$ be the probabilities the label is neutral, contradiction or entailment. The coordinate of the prediction $\mathbf{C_p}$ in the triangle is computed as $\mathbf{C_p} = p_1\mathbf{C_1}+p_2\mathbf{C_2}+p_3\mathbf{C_3}$.
In the triangle, the distinctly colored background (grey, light grey, and light green) indicates the regions that correspond to different labels. The prediction result for the original sentence pair is represented by the larger yellow circle, whereas the smaller gray circles illustrate the perturbed sentence pairs. A density contour of the prediction is computed to emphasize the highly cluttered areas and distinguish the outliers.

### 2018-06-09 paper/relatedWorks.tex
fix typos

\textbf{Visual Exploration of Neural Network Models.}
Due to the effectiveness of exploring complex relationships, visualization has long been adopted for interpreting neural network models~\cite{TzengMa2005}.
Recently, the increasing demand for interpretability for machine learning models has motivated the introduction of many visualization works that are dedicated to neural network models.
% The classification~\cite{KrausePererNg2016}
%The Prospector~\cite{KrausePererNg2016} provides a model agnostic approach for analyzing and interpreting predictions via an interactive visual interface.
%
In the work~\cite{BilalJourablooYe2018} by Bilal et al., the authors analyzed classification errors in convolutional neural networks (CNN) and answered the question of whether class hierarchy is learned in the network.
%
The DeepEyes~\cite{Pezzotti2018} focused on analyzing the training process of CNN, which provided domain experts design guideline of the deep neutral network architecture.
%
The ActiVis~\cite{KahngAndrewsKalro2018} introduced an interactive system tailored for tuning industry-scale neural networks in Facebook.
The TensorFlow Graph Visualizer~\cite{Wongsuphasawat2018} work designed a hierarchical visual representation to encode complex computation graphs of deep neural networks for the TensorFlow framework~\cite{Abadi2016}.
Finally, Liu et al.~\cite{LiuShiCao2018} presented a visualization tool for understanding the often challenging training process of deep generative models.

>>>>

\textbf{Visual Exploration of Neural Network Models.}
Due to the effectiveness of exploring complex relationships, visualization has long been adopted for interpreting neural network models~\cite{TzengMa2005}.
Recently, the increasing demand for interpretability for machine learning models has motivated the introduction of many visualization work that are dedicated to neural network models.
% The classification~\cite{KrausePererNg2016}
%The Prospector~\cite{KrausePererNg2016} provides a model agnostic approach for analyzing and interpreting predictions via an interactive visual interface.
%
In the work~\cite{BilalJourablooYe2018} by Bilal et al., the authors analyzed classification errors in convolutional neural networks (CNN) and answered the question of whether class hierarchy is learned in the network.
%
The DeepEyes~\cite{Pezzotti2018} focused on analyzing the training process of CNN, which provided domain experts design guideline of the deep neutral network architecture.
%
The ActiVis~\cite{KahngAndrewsKalro2018} introduced an interactive system tailored for tuning industry-scale neural networks in Facebook.
The TensorFlow Graph Visualizer~\cite{Wongsuphasawat2018} work designed a hierarchical visual representation to encode complex computation graphs of deep neural networks for the TensorFlow framework~\cite{Abadi2016}.
Finally, Liu et al.~\cite{LiuShiCao2018} presented a visualization tool for understanding the often challenging training process of deep generative models.
